---
output: github_document
html_preview: false
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    warning = FALSE,
    fig.path = "README-"
)
```


# QSync (in development)

This package contains a suite of functions to simplify the synchronisation (merging and duplicate control) of shared datasets used by several co-workers using individual projects that are processed with [QGIS](https://www.qgis.org/) and/or [QField](https://github.com/opengisch/QField/). 

***
## Install package

```{r, eval=FALSE}
devtools::install_github("mottensmann/QFieldSync")
```

## Load package once installed

```{r}
## load package
library(QFieldSync)
```


## Merging observations

### Prerequisites:

Merging observations recorded in separate QGIS projects requires that the following attributes/fields are configured:

* (1) [uuid](https://en.wikipedia.org/wiki/Universally_unique_identifier): a *universal-unique-identifier* identifying each record.
* (2) [MTIME](https://www.fosslinux.com/121740/linux-file-timestamps-how-to-use-atime-mtime-and-ctime.htm): *Modification Time*, time-stamp denoting the last modification of a record*

### `db_unique` function

The function `db_unique` allows to identify and subsequently remove duplicated entries from the database. For each identical record - sharing the same uuid - always the most recently updated case is selected based on the MTIME attribute. Older records are removed.

Create a simple non-spatial dataset for illustration purposes:

```{r}
## code a toy dataset: Ten obseravation A:J
(db <- data.frame(uuid = LETTERS[1:10], MTIME = Sys.time()))

## now duplicate record J and update MTIME value
db <- rbind(db,db[10,])
db[11, "MTIME"] <- db[11, "MTIME"] + 60*60
db
```

Handle duplicated entry J (indices 10 and 101):

```{r}
## removes the older record (index 10)
(db <- db_unique(db))
```

Example using GeoPackage layers:

```{r}
## load example datasets: 
path <- "~/../QField/cloud/BsGtBi_Projekte/bsgtbi/"
QField_1 <-  sf::read_sf(file.path(path, 'bsgtbi_mo/Avifauna.gpkg'), 'Aves') 
dim(QField_1)
QField_2 <-  sf::read_sf(file.path(path, 'bsgtbi_bw/Avifauna.gpkg'), 'Aves') 
dim(QField_2)

## merge data frames
db <- rbind(QField_1, QField_2)
dim(db)
db <- db_unique(db)
dim(db)

## export to GeoPackage (NOT RUN)
# sf::st_write(
#   db, 
#   dsn = file.path(pfad_cloud, "Avifauna.gpkg"),
#   layer = 'Aves',
#   layer_options = "OVERWRITE=YES",
#   append = FALSE)
```

